\vspace*{-1.5em} \rule{\textwidth}{0.4pt} \\[0.4em] \textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification} \\[0.4em] \rule{\textwidth}{0.4pt}

### 2025-01-20 paper/main.tex
geographically decentralized

  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on succinct proofs and multi-party inference to verify LoRA–base model compatibility without exposing LoRA weights. ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on state-of-the-art large language models. This low-latency approach enables nearly real-time verification and promotes secure collaboration among geographically dispersed teams and contract-based training pipelines. The protocol ensures that the delivered LoRA module works as claimed, safeguarding the contributor’s intellectual property while providing the base model user with verification of compatibility and lineage.
\end{abstract}

>>>>

  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on succinct proofs and multi-party inference to verify LoRA–base model compatibility without exposing LoRA weights. ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on state-of-the-art large language models. This low-latency approach enables nearly real-time verification and promotes secure collaboration among geographically decentralized teams and contract-based training pipelines. The protocol ensures that the delivered LoRA module works as claimed, safeguarding the contributor’s intellectual property while providing the base model user with verification of compatibility and lineage.
\end{abstract}
